Pyro-Velocity

### 2024-07-19 nbs/guides/installation.qmd
nit(installation): note requirement to activate virtual env
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>
chore(nbs): interlink introductory pages
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

```bash
echo "3.10" > .python-version
uv python install
uv venv -p 3.10
uv pip install pyrovelocity
```

@@

>>>>

```bash
echo "3.10" > .python-version
uv python install
uv venv -p 3.10
source .venv/bin/activate
uv pip install pyrovelocity
```

@@

After the installation has completed successfully you may like to see

- [Introduction](/tutorials/introduction.qmd) for a brief overview
- [Usage](/templates/user_example/user_example.qmd) for a complete usage example 
- [Contributing](/about/contributing.qmd) for information on how to setup a development environment

### 2024-07-19 nbs/tutorials/introduction.qmd
chore(nbs): interlink introductory pages
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

>>>>

This document provides a brief overview of what Pyro-Velocity is and how it can be used.
See

- [Installation](/guides/installation.qmd) for installation instructions or
- [Usage](/templates/user_example/user_example.qmd) for a complete usage example
- [Contributing](/about/contributing.qmd) for information on how to setup a development environment
